---
title: "Untitled"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns 
    vertical_layout: fill
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = FALSE, message = FALSE)
```

```{r echo=F}
library(tidyverse)
library(crosstalk)
library(flexdashboard)
# INformation
#https://rstudio.github.io/DT/
#https://bookdown.org/yihui/rmarkdown/layout.html
```

Interactives {data-icon="ion-stats-bars"}
=====================================  

Column {data-width=300}
-------------------------------------

### Filters

```{r}
# Load data
gene_table <- readxl::read_excel(path = "data/Tabela Mandar Daniel.xlsx")
# Make shared object
sd <- SharedData$new(gene_table)
```

```{r}
# Selectors
filter_select(
    id = "gene_name",
    label = "Gene Name:",
    sharedData = sd,
    group = ~Gene)
filter_select(
    id = "protein_name",
    label = "Protein Name:",
    sharedData = sd,
    group = ~Name)
filter_select(
    id = "Phage",
    label = "Phage Name:",
    sharedData = sd,
    group = ~Phage)

```

Column {data-width=600}
-------------------------------------

### Datatable
    

```{r datatable}

sd %>% 
  DT::datatable(
    filter = "top",  # allows filtering on each column
    extensions = c(
      "Buttons"  # add download buttons, etc
      #"Scroller"  # for scrolling down the rows rather than pagination
    ),
    caption = "Caption to see how it looks",
    class = 'cell-border stripe',
    rownames = FALSE,  # remove rownames
    style = "bootstrap",
    #class = "compact",
    #width = "100%",
    fillContainer = T,
    options = list(
      dom = "lrBtip",  # specify content (search box, etc)
      deferRender = TRUE,
      scrollY = 700,
      scroller = F,
      autoWidth = TRUE,
      columnDefs = list(
        list(
          visible = FALSE,
          targets = c(2, 3, 5:15),
          width = "20"
        )
      ), 
      buttons = list(
        I("colvis"),  # turn columns on and off
        "csv",  # download as .csv
        "excel"  # download as .xlsx
      )
    ),
    colnames = c(
      "Gene" = "Gene",
      "Protein Name" = "Name",
      "Expression" = "Expression",
      "Fold Change" = "Foldchange",
      "Number" = "Number",
      "P-value" = "Pvalue",
      "P-adjusted" = "Padjusted",
      "Approach" = "Approach",
      "Technique" = "Technique",
      "Host Bacteria" = "Bacteria",
      "Medium" = "Medium",
      "Hours post infection" = "Hours post infection",
      "Phage" = "Phage",
      "Strain" = "Strain",
      "MOI" = "MOI",
      "Study Title" = "PAPER",
      "Year" = "Year",
      "Reference" = "Reference",
      "DOI" = "DOI"
    )
  )
```

Information {data-orientation=rows data-icon="fa-info-circle"}
===================================== 

### How to use
#### Filters

You can:

* select one or more local authorities from the dropdown menu (remove them with your backspace key)
* select one or more Ofsted grades using the checkboxes
* select the phase of education with the checkboxes
* drag the slider to select a pupil count
* drag the slider to filter by the percenatge of pupils receiving free school meals

#### Interactive table

You can:

* filter each column by typing in the boxes under each column header
* sort the columns (ascending and descending) by clicking on the column header
* change which columns are visible by clicking the Column visibility button
* click 'CSV' or 'Excel' to download the filtered data to a .csv file or a .xlsx
* see how many entries remain after filtering in the bottom-left, where it says 'Showing X to Y of Z entries'

### Tools

[R v3.4.4](https://www.r-project.org/) and [RStudio v1.1.442](https://www.rstudio.com/) were used to build this tool.

The packages used were:

* [Flexdashboard](https://rmarkdown.rstudio.com/flexdashboard/) to create a frame for the content
* [Leaflet](https://rstudio.github.io/leaflet/) for the interactive map
* [DT](https://rstudio.github.io/DT/) for the interactive table
* [Crosstalk](https://rstudio.github.io/crosstalk/) for widget interactivity
* [Ion icons](https://ionicons.com/) and [Font Awesome](https://fontawesome.com/) for icons

The code for this tool is available from 
